### 2019-02-20 experiments.tex
info on new experiment

>>>>

\subsubsection{Visible Value vs. Final State Nondeterminism}

We also used {\tt redis-py} to investigate the tradeoff between
overhead and ability to detect nondeterminism when using the two
proposed approaches to horizontal determinism.  We produced 300 tests
of length 100, using the known-nondeterministic version of the {\tt
  redis-py} harness.  We then used {\tt nondeterministic} and {\tt
  stepNondeterministic} calls, both with a delay of 0.005 seconds and
a single additonal execution of the test, to
check these tests for nondeterministic behavior.  Final state
nondeterminism actually detected one instance of nondeterminism that
visible value nondeterminism failed to detect; in general, final state
nondeterminism is less able to detect nondeterminism, but in this
instance the difference is less important than the nondeterminism of
whether a particular test will exhibit nondeterministic behavior in a
single run.  This difference is obviously not statistically
significant; for the nondeterminism in {\tt redis-py}, with these
parameters, the two approaches cannot be statistically distinguished
as to effectiveness in detecting nondeterminism.

Final state nondeterminism was also faster; visible value
nondeterminism took, on average, 0.48\% longer to check for
nondeterminism on the 300 tests.  The difference was significant, with
$p$-value $< 1.19 \times 10^{-23}$ by a paired Wilcoxon test.
